---
title: "Introduction to pgmcs"
author: "Zhuoer Dong"
date: "`r Sys.Date()`"
output: prettydoc::html_pretty
vignette: >
  %\VignetteIndexEntry{Introduction to pgmcs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", cache = TRUE)
```



```{r}
library(pgmcs)

suppressWarnings(RNGversion('3.5.2'))
```



# Web App

The package is very simple to use, all you need is a browser, like Chrome.

- [dynamic mode](https://dongzhuoer.shinyapps.io/population-genetics-monte-carlo-simulation/)
- [static mode](https://dongzhuoer.shinyapps.io/population-genetics-monte-carlo-simulation2/)

But if you can't stand the low speed, and the unstable connection demanding frequent refresh, you may consider the following approach.



# Run on your own computer

In this way, you can free from the above troubles. It's very easy, you just need to install R, which is even simpler than QQ.

1. install [R](https://www.r-project.org/) (use [this](https://cran.r-project.org/bin/windows/base/) for Windows users.)

2. open R and install this package

```r
if (!('remotes' %in% .packages(T))) install.packages('remotes');
remotes::install_github('dongzhuoer/pgmcs');
```

3. open R and run the application

```r
shiny::runApp(system.file('shiny/pgmcs', package = 'pgmcs'))
shiny::runApp(system.file('shiny/pgmcs2', package = 'pgmcs'))
```



# Command line interface

If you are familiar with R, you can get rid of the limit on population size and generation number, and try whatever parameters you like. 

```{r}
set.seed(0);
demo_population_simulation(100, 250, c(0, 490, 10), c(1, 1, 1), 'drift')
demo_population_simulation(100, 250, c(0, 490, 10), c(1, 1, 0.95), 'select A')
```

The following code reproduce the figures in 20.2 of _Genetics From Genes to Genomes, 5th_


## Figure 20.8 at P671

Initial population are all heterozygotes.

```{r}
set.seed(13);
demo_population_simulation(6, 30, c(0, 10, 0), c(1, 1, 1), "Small population: Lots of genetic drift");
```

```{r}
set.seed(0);
demo_population_simulation(6, 30, c(0, 500, 0), c(1, 1, 1), "Large population: Little genetic drift");
```


## Figure 20.13 at P676

499*bb + 1*Bb; WBB = 1.0, WBb = 1.0, Wbb = 0.98 (adjusted to 0.97)

```{r}
set.seed(885);  # 57
demo_population_simulation(6, 900, c(0, 1, 499), c(1,1,0.97), "Natural selection together with genetic
drift")
```
